Model

### 2019-05-29 stats/model.Rmd
add second model run

sem_know_model<- webppl(
  program_code = paste(rsaUtils, rsaModel, semStr , sep='\n'),
  data = list(data = me_model_data),
  data_var = "dataFromR",
  model_var = "model",
  chains = 3,
  cores = 3,
  inference_opts = list(method = "incrementalMH", 
                        samples = 6000, 
                        burn = 2000,
                        verbose = T,
                        lag = 1,
                        verboseLag = 1000)
)

#saveRDS(sem_know_model, "../saves/sem_know_model.rds")
sem_know_model <- readRDS("../saves/sem_know_model.rds")

@@

```{r}
ggarrange(data_plot,model_plot,glmm_plot, common.legend = T, legend = "right", nrow = 1, ncol = 2)
```

@@

novel_bm <- brm(correct ~ age_num + (1 | subid) + (age_num | agent), 
          data = novel_data, family = bernoulli(),
          control = list(adapt_delta = 0.95),
          sample_prior = F,
          save_all_pars = F,
          iter = 10000)

>>>>

sem_know_model<- webppl(
  program_code = paste(rsaUtils, rsaModel, semStr , sep='\n'),
  data = list(data = me_model_data),
  data_var = "dataFromR",
  model_var = "model",
  chains = 8,
  cores = 8,
  inference_opts = list(method = "incrementalMH", 
                        samples = 4000, 
                        burn = 2000,
                        verbose = T,
                        lag = 1,
                        verboseLag = 1000)
)

#saveRDS(sem_know_model, "../saves/sem_know_model.rds")
sem_know_model <- readRDS("../saves/sem_know_model.rds")
```

@@

```{r}
ggarrange(data_plot,model_plot,glmm_plot, common.legend = T, legend = "right", nrow = 1, ncol = 3)
```

@@

# novel_bm <- brm(correct ~ age_num + (1 | subid) + (age_num | agent), 
#           data = novel_data, family = bernoulli(),
#           control = list(adapt_delta = 0.95),
#           sample_prior = F,
#           save_all_pars = F,
#           iter = 10000)
# 
# saveRDS(novel_bm, "../saves/novelty_model.rds")

novel_bm <- readRDS("../saves/novelty_model.rds")
